### 2023-04-23 main.tex
lll

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}\,.
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$, $\lambda_i\geq \lambda_{i+1}$ and $\sum_{i=1}^N \lambda_i = \nu$.  
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
\end{equation} 
The dimension $M_\twoj$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
\end{equation}
%where $\sum_{a=1}^{N}n_{i}=\nu$. 
The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle
	\end{cases}\,.
\end{equation}  
The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
{\color{red} Is this remark relevant for us?}
\newline 
\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	\mathcal{H}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
\end{equation}
where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
the edge $(x,y)\in \mathcal{E}$.

>>>>

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}\,.
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_i\geq \lambda_{i+1}$,  $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.  
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
\end{equation} 
The dimension $M_\twoj$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The generators of the symmetric representations will be denoted by $E_{ab}$.
The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
\end{equation}
%where $\sum_{a=1}^{N}n_{i}=\nu$. 
The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle
	\end{cases}\,.
\end{equation}  
The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
{\color{red} Is this remark relevant for us?}
\newline 
\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
The process with generator \eqref{Generator} can be described in terms of $gl(n)$ Lie algebra generators. The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site, namely
%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
{\color{blue}
where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.}
{\color{red}remove?}
The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
\end{equation}

{\color{red}Maybe some more text below}
We introduce the Hamiltonian operator
\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian that describes the interaction between two connected sites is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
{\color{red} no minus sign?}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}\,.
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	\mathcal{H}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
\end{equation}
where $\Delta^{x,y}(C_2)$ denotes a {\color{blue}copy} of $\Delta(C_2)$ acting on  
the edge $(x,y)\in \mathcal{E}$.
